Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-04-05 Paper.tex
Specify empty round brackets in Appendix D

We also assume a function $n$, the trie's node cap function. When composing a node, we use RLP to encode the structure. As a means of reducing storage complexity, we store nodes whose composed RLP is fewer than 32 bytes directly; for those larger we assert prescience of the byte array whose Keccak-256 hash evaluates to our reference. Thus we define in terms of $c$, the node composition function:
\begin{equation}
n(\mathfrak{I}, i) \equiv \begin{cases}
() & \text{if} \quad \mathfrak{I} = \varnothing \\
c(\mathfrak{I}, i) & \text{if} \quad \lVert \, \texttt{RLP} \big( c(\mathfrak{I}, i) \big) \rVert < 32 \\
\texttt{KEC}\big(\texttt{RLP}( c(\mathfrak{I}, i)) \big) & \text{otherwise}
\end{cases}
\end{equation}

@@

A branch is then only used when necessary; no branch nodes may exist that contain only a single non-zero entry. We may formally define this structure with the structural composition function $c$:
\begin{equation}
c(\mathfrak{I}, i) \equiv \begin{cases}
 \big(\texttt{HP}(I_0[i .. (\lVert I_0\rVert - 1)], 1), I_1 \big) & \text{if} \quad \lVert \mathfrak{I} \rVert = 1 \quad \text{where} \; \exists I: I \in \mathfrak{I} \\
\big(\texttt{HP}(I_0[i .. (j - 1)], 0), n(\mathfrak{I}, j) \big) & \text{if} \quad i \ne j \quad \text{where} \; j = \max \{ x : \exists \mathbf{l}: \lVert \mathbf{l} \rVert = x \wedge \forall I \in \mathfrak{I}: I_0[0 .. (x - 1)] = \mathbf{l} \} \\
(u(0), u(1), ..., u(15), v) & \text{otherwise} \quad \text{where} \begin{array}[t]{rcl}
u(j) & \equiv & n(\{ I : I \in \mathfrak{I} \wedge I_0[i] = j \}, i + 1) \\
v & = & \begin{cases}
I_1 & \text{if} \quad \exists I: I \in \mathfrak{I} \wedge \lVert I_0 \rVert = i \\
() & \text{otherwise}
\end{cases}
\end{array}
\end{cases}
\end{equation}

>>>>

We also assume a function $n$, the trie's node cap function. When composing a node, we use RLP to encode the structure. As a means of reducing storage complexity, we store nodes whose composed RLP is fewer than 32 bytes directly; for those larger we assert prescience of the byte array whose Keccak-256 hash evaluates to our reference. Thus we define in terms of $c$, the node composition function:
\begin{equation}
n(\mathfrak{I}, i) \equiv \begin{cases}
() \in \mathbb{B} & \text{if} \quad \mathfrak{I} = \varnothing \\
c(\mathfrak{I}, i) & \text{if} \quad \lVert \, \texttt{RLP} \big( c(\mathfrak{I}, i) \big) \rVert < 32 \\
\texttt{KEC}\big(\texttt{RLP}( c(\mathfrak{I}, i)) \big) & \text{otherwise}
\end{cases}
\end{equation}

@@

A branch is then only used when necessary; no branch nodes may exist that contain only a single non-zero entry. We may formally define this structure with the structural composition function $c$:
\begin{equation}
c(\mathfrak{I}, i) \equiv \begin{cases}
 \big(\texttt{HP}(I_0[i .. (\lVert I_0\rVert - 1)], 1), I_1 \big) & \text{if} \quad \lVert \mathfrak{I} \rVert = 1 \quad \text{where} \; \exists I: I \in \mathfrak{I} \\
\big(\texttt{HP}(I_0[i .. (j - 1)], 0), n(\mathfrak{I}, j) \big) & \text{if} \quad i \ne j \quad \text{where} \; j = \max \{ x : \exists \mathbf{l}: \lVert \mathbf{l} \rVert = x \wedge \forall I \in \mathfrak{I}: I_0[0 .. (x - 1)] = \mathbf{l} \} \\
(u(0), u(1), ..., u(15), v) & \text{otherwise} \quad \text{where} \begin{array}[t]{rcl}
u(j) & \equiv & n(\{ I : I \in \mathfrak{I} \wedge I_0[i] = j \}, i + 1) \\
v & = & \begin{cases}
I_1 & \text{if} \quad \exists I: I \in \mathfrak{I} \wedge \lVert I_0 \rVert = i \\
() \in \mathbb{B} & \text{otherwise}
\end{cases}
\end{array}
\end{cases}
\end{equation}
